 \section{Список літератури}
\begin{enumerate}

\item{{\it Cvetkovic D., Doob M., Sachs H.,} Spectra of Graphs, 1980.}

\item{{\it Cvetkovic D., Doob M., Gutman I., Torgasev A.,} Recent Results in the Theory of Graph Spectra, in: Annals of Discrete Mathematics, vol.36, North
Holland, Amsterdam, 1988.}

\item{{\it Cvetkovic D., Rowlinson M., Simic S.,} Eigenspaces of graphs, Cambridge University Press, 1997.}


\item{{\it Cvetkoviс D. M.} Applications of graph spectra, in: Zbornik radova, 2009, 13(21), 138pp.}

\item{{\it Цветкович Д., Дуб М., Захс Х.,}Спектры графов, теория и
применение Киев, ``Наукова думка'', 1984.}

\item{{\it Chung F.R.K.,} Spectral Graph Theory, AMS, Providence,
RI,  1994}

\item{{\it Gladwell G.M.L.,} Inverse Problems in Vibration, in: Kluwer Academic Publishers,New York, 2005,457pp.}

\item{{\it Харари Ф.,} Теория графов, ``Мир'', Москва, 1973.}

\item{{\it Оре О.,} Теория графов, ``Наука'', Москва, 1980.}

\item{{\it Bondy J.A., Murty U.S.R.,} Graph Theory with Applications graphs
, American Elsevier Publishing Company, Inc., New York, 1976}

\item{{\it Harary F.,} The determinant of the adjacency matrix of a
graph, SIAM Rev., 4 (1962), 202-210}

\item{{\it H. Sachs,} Beziehungen zwischen den in einem graphen enthaltenen
kreisen und seinem charakteristischen polynom, Publ. Math. Debrecen,
11 (1964), 119–134.}

\item{{\it Schwenk A. J.}, Computing the characteristic polynomial of a graph, Graphs and Combinatorics, volume 406 of Lecture Notes in Mathematics, pages 153-172. AMS, Springer, Berlin, Heidelberg, New York, 1974.}


\item{{\it Тимошкевич Лариса Миколаївна,} Прямі та обернені спектральні задачі зважених скінченних графів і зліченних графів Кокстера.- Дисертація канд. фіз.-мат. наук: 01.01.06, Київ. нац. ун-т ім. Тараса Шевченка. - Київ, 2015.- 160 с.} 
\end{enumerate}
